---
title: "Paper data and tables and fig"
author: "Ravi Joshi"
date: "8/5/2021"
output: pdf_document
getwd()
df_all_numeric <- read.csv("final_hmd_bbd_census_numeric.csv")
install.packages("ggplot2")
library("ggplot2")
install.packages("data.table")           # Install and load data.table
library("data.table")
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#install.packages("stargazer") #Use this to install it, do this only once
library(stargazer)
getwd()
```{r}
df_county_year <- read.csv("Filter_final_data_countyid_paper.csv")
dfrmdhmdacensus <- read.csv("Filter_final_data_paper_Hmdacensus.csv")
dfrmdhmdacensus$amountofloan <- (dfrmdhmdacensus$amountofloan)*1000
dfrmdhmdacensus <- dfrmdhmdacensus[,-1]
head(dfrmdhmdacensus)
```

```{r}
-------------------Filter Data-------------------------
df_filter_hmda_paper <- sqldf("select * from dfrmdhmdacensus where Credit_Score>= 620 and Credit_Score<= 850 and applicantincome >= 30000 and applicantincome <= 300000 and amountofloan >= 50000 and amountofloan <= 700000 and Original_DTI_Ratio >= 5 and Original_DTI_Ratio <= 70 and Original_Combined_LTV >= 20 and Original_Combined_LTV <= 120 and property_val<= 2000000 ;")
head(df_filter_hmda_paper)
```
head(df_all_numeric)

```{r}
race_eth_data_1 <- sqldf("SELECT *  from df_all_numeric  where derived_race not in ('Race Not Available','Free Form Text Only', 'Joint', '2 or more minority race')
and derived_ethnicity not in ('Ethnicity Not Available','Free Form Text Only', 'Joint');")
##grep("ratio", colnames(race_eth_data_1))
##colnames(race_eth_data_1)[69] <- "BBD Penetration"
race_eth_data_1$ Credit_Score <- (race_eth_data_1$Credit_Score)*100
race_eth_data_1$ applicantincome <- (race_eth_data_1$applicantincome)*1000
race_eth_data_1$ amountofloan <- (race_eth_data_1$amountofloan)*1000
final_race_eth_data <- sqldf("select * from race_eth_data_1 where Credit_Score>= 620 and Credit_Score<= 850 and applicantincome >= 30000 and applicantincome <= 300000 and amountofloan >= 50000 and amountofloan <= 700000 and Original_DTI_Ratio >= 5 and Original_DTI_Ratio <= 70 and Original_Combined_LTV >= 20 and Original_Combined_LTV <= 120 and property_val<= 2000000 ;")

final_race_eth_data$ Credit_Score <- (final_race_eth_data$Credit_Score)/100

summary(final_race_eth_data$Credit_Score)
```

```{r}
df_county_year <- read.csv("Filter_final_data_countyid_paper.csv")
stargazer(df_county_year[c("Credit_Score","applicantincome","amountofloan","Original_Interest_Rate","Original_DTI_Ratio","Original_Combined_LTV","Original_UPB","property_val","poverty_percentage","est_population","derived_race","combined_loan_to_value_ratio","year","ratio","absolute_penetration","ratio_ms_usage")], type = "text",
title="Descriptive statistics County level Table 2",digits=1, out="table2.txt")
```

```{r}
head(dfrmdhmdacensus)
stargazer(df_filter_hmda_paper[c("Credit_Score","applicantincome","amountofloan","Original_Interest_Rate","diff_interest_mean","Original_DTI_Ratio","diff_interest_median","Original_Combined_LTV","property_val", "year")], type = "latex",title="Descriptive statistics individual level Table 1",digits=1, out="New Table 1.txt")

```

```{r}

df_population_penetration_all_years <- read.csv("df_final_income_population.csv")
 install.packages("sqldf")
 library("sqldf")
 data_bbd_filter_18_20 <- sqldf(" select countyid, year, ratio from df_all_numeric where year in (2018,2019,2020) group by year, countyid ;")
 nrow(data_bbd_filter_18_20)
 unique(data_bbd_filter_18_20$year)
 data_bbd <- sqldf("SELECT year, AVG(ratio) AS broadband_penetration from df_population_penetration_all_years where year in (2016,2017) and month = 6 group by year
 UNION
 select year, AVG(ratio) AS broadband_penetration from data_bbd_filter_18_20 group by year;")
 
 p <- ggplot(data= data_bbd, aes(x=year, y= broadband_penetration),color="Red")+ geom_line()+ggtitle("") +
  xlab("Year") + ylab("Broadband Penetration")
plot(p)
```
str(df_population_penetration_all_years)
```{r}
data_bbd_filter_all_year <- sqldf(" select year, ratio from df_population_penetration_all_years where year in (2009,2010,2011,2012,2013,2014,2016,2016,2017,2018) and month = 6 group by year ;")
data_bbd_filter_all_year$ratio <- as.numeric(data_bbd_filter_all_year$ratio)
str(data_bbd_filter_all_year)
                  ##### Normal Density and Histogram#################

r <- data_bbd_filter_all_year$ratio
head(r)
m<-mean(r)
std<-sqrt(var(r))
hist(r, density=20, breaks=2, prob=TRUE, 
     xlab="Broadband Penetration", ylim=c(0,4), 
     main="",cex.lab=0.75, cex.axis=0.75, cex.main=0.75, cex.sub=0.75)
curve(dnorm(x, mean=m, sd=std), 
      col="darkred", lwd=2, add=TRUE, yaxt="n")


```
```{r}
df_map_2018 <- sqldf("select * from data_bbd_filter_18_20 where year=2018;")
df_map_2019 <- sqldf("select * from data_bbd_filter_18_20 where year=2019;")
df_map_2020 <- sqldf("select * from data_bbd_filter_18_20 where year=2020;")
head(df_map_2018)
df_map_2018$fips <- df_map_2018$countyid 
df_map_2019$fips <- df_map_2019$countyid
df_map_2020$fips <- df_map_2020$countyid
df_map_2018$R18 <- df_map_2018$ratio
df_map_2019$R19 <- df_map_2019$ratio
df_map_2020$R20 <- df_map_2020$ratio
df_map_union_2018_2019 <- sqldf("select * from df_map_2018 a left join df_map_2019 b on a.fips=b.fips ;")
nrow(df_map_2019)
head(df_map_union_2018_2019)
df_map_union_2018_2019 <- df_map_union_2018_2019[,-6]

filter_map_20182019 <- sqldf("select * from df_map_union_2018_2019 where R19 is not NULL;")
head(filter_map_20182019)


filter_map_20182019$Percent.Change18_19 <- (filter_map_20182019$R19 - filter_map_20182019$R18)*100/filter_map_20182019$R18

head(filter_map_20182019)
--------------------------2019-2020---------------------------------------
df_map_union_2019_2020 <- sqldf("select * from df_map_2019 a left join df_map_2020 b on a.fips=b.fips ;")
head(df_map_union_2019_2020)

df_map_union_2019_2020 <- df_map_union_2019_2020[,-6]
filter_map_2019_2020 <- sqldf("select * from df_map_union_2019_2020 where R20 is not NULL;")
filter_map_2019_2020$Percent.Change19_20 <- (filter_map_2019_2020$R20 - filter_map_2019_2020$R19)*100/filter_map_2019_2020$R19
head(filter_map_2019_2020)
```
---------------------Map ---19--20----------------------------------
```{r}
install.packages("usmap")
library("us.map")
plot_usmap(data = filter_map_2019_2020, values = "R20") + scale_fill_continuous(
    low = "green", high = "magenta",
  name = "Broadband Penetration 2020", label = scales::comma) + 
  theme(legend.position = "top")
``` 
  
-----------------------------18-20---------------------------------------------------
```{r}
df_map_union_2018_2020 <- sqldf("select * from df_map_2018 a left join df_map_2020 b on a.fips=b.fips ;")
df_map_union_2018_2020 <- df_map_union_2018_2020[,-6]
filter_map_2018_2020 <- sqldf("select * from df_map_union_2018_2020 where R20 is not NULL;")
filter_map_2018_2020$Change1820 <- (filter_map_2018_2020$R20 - filter_map_2018_2020$R18)*100/filter_map_2018_2020$R18
head(filter_map_2018_2020)

df_filter_map_change_25<- sqldf("select * from filter_map_2018_2020 where Change1820 < 25 ;")
 df_filter_map_change_40_100<- sqldf("select * from filter_map_2018_2020 where Change1820 >=40 and Change1820<=100;")
 df_filter_map_change_25_40<- sqldf("select * from filter_map_2018_2020 where Change1820 >=25 and Change1820 <40 ;")
 
  df_filter_map_change_100_800<- sqldf("select * from filter_map_2018_2020 where Change1820 > 100 and Change1820<800;")
head(filter_map_2018_2020)
```

```{r}
temp <- data.table(filter_map_2018_2020)
temp[,bb_change_category:= ifelse(Change1820<25,"1. Less than 25",ifelse(Change1820<40,"2. 25-to 40",
ifelse(Change1820<100,"3. 40-100","4. More than 100")))]
head(temp)
temp_join <- join_all(list (dfrmdhmdacensus,temp), by=c('countyid','year'), type='left')
felm(Original_Interest_Rate ~ Change1820+Credit_Score+Original_DTI_Ratio|year,data=temp_join)
  stargazer(temp_join,title="Regression Results",single.row= TRUE, align=TRUE,type="text",intercept.bottom = FALSE, out="temp.txt")
head(temp_join)

```



```{r}
 -----------------------------Change Col Names--------------------------
head(df_filter_map_change_25)
head(df_filter_map_change_40_100)
head(df_filter_map_change_25_40)
head(df_filter_map_change_100_800)
colnames(df_filter_map_change_25)[10] <- "change_25"
colnames(df_filter_map_change_40_100)[10] <- "change_40100"
colnames(df_filter_map_change_25_40)[10] <- "change_2540"
colnames(df_filter_map_change_100_800)[10] <- "change_100"
```
------------------------------------race ethnicity data1---------------------------

-

--------------------------------Join map bbd data final regression------------------
```{r}
library(dplyr)
df25 <- select(df_filter_map_change_25, -(ratio:R20))
df2540<- select(df_filter_map_change_25_40, -(ratio:R20))
df40100<- select(df_filter_map_change_40_100, -(ratio:R20))
df100<- select(df_filter_map_change_100_800, -(ratio:R20))
library(plyr)
y <- join_all(list (race_eth_data_1,df2540), by=c('countyid','year'), type='left')
z <- join_all(list (y,df40100), by=c('countyid','year'), type='left')
y1 <- join_all(list (z,df25), by=c('countyid','year'), type='left')
z1 <- join_all(list (y1,df100), by= c('countyid','year'), type='left')
z1$fips <- z1$countyid
su(z1)
----------------------------------------------------------------------------------------
df_z1 <- sqldf("select *, 
                CASE when change_25 is not null then ch25
                CASE when change_2540 is not null then ch2540
                CASE when change_40100 is not null then ch40100
                CASE when change_100 is not null then ch100
                ELSE NULL END AS ch_flag
 from z1")

 
 
------------------------------- Regression----------------------------------
regress_tab_bbd <- felm(amountofloan ~ change_2540|year, data= z1)

stargazer(regress_tab_bbd,title="Regression Results",single.row= TRUE, align=TRUE,type="text", out="new broadband.txt")
str(df_filter_map_change_100_800)
```



```{r}
-------------------------Plot US Map------------------------------------
install.packages("usmap")
library("usmap")
df_filter_map_change_60_750<- sqldf("select * from filter_map_2018_2020 where Change1820 >=60 and Change1820 < 750 ;")
df25$fips <- df25$countyid
df2540$fips <- df2540$countyid
df40100$fips <- df40100$countyid
df100$fips <- df100$countyid

head(df_filter_map_change_60_750)
plot_usmap(data = df_filter_map_change_60_750, values = "Change1820") + scale_fill_continuous(
    low = "green", high = "magenta",
  name = "Broadband Percent Change > 60", label = scales::comma) + 
  theme(legend.position = "top")
  ```
  
 ------------------------------------------------------------------------------------- 
  --------------------Regression UPB~ credit+x+y+z------------------------
  ```{r}
  install.packages("Matrix")
  install.packages("dcolumn")
  library("dcolumn")
  head(df_all_numeric)
  library(lfe)
  regress_tab3 <- felm(Original_UPB ~ Credit_Score+Original_DTI_Ratio+Original_LTV+applicantincome |countyid , data= df_all_numeric)
stargazer(regress_tab3,title="Regression Results",single.row= TRUE, align=TRUE,type="text", out="regtab3.txt")

-------------------Regression Interest Rate ~ credit+x+y+z------------------------
  install.packages("Matrix")
  install.packages("dcolumn")
  library("dcolumn")
  head(df_all_numeric)
  nrow(df_all_numeric)
  library(lfe)
  regress_tab4 <- felm(interest_rate ~ Credit_Score+Original_DTI_Ratio+applicantincome |year, data= df_all_numeric)
 stargazer(regress_tab4,title="Regression Results",single.row= TRUE, align=TRUE,type="text", out="regtab4.txt")
   -------------------------------BBD----------------------------------------------
   regress_tab6 <- felm(interest_rate~ ratio+Credit_Score+Original_DTI_Ratio+applicantincome |year, data= final_race_eth_data)
   stargazer(regress_tab6,title="Regression Results",single.row= TRUE, align=TRUE,type="text",covariate.labels = c("Broadband Penetration"),omit.stat=c("ser"),intercept.bottom = FALSE, out="regtab6.txt")
**********************************************************************************************
   stargazer(output, output2, type = "html", 
          title            = "These are awesome results!",
          covariate.labels = c("Temperature", "Wind speed", "Rain (inches)",
                               "2nd quarter", "3rd quarter", "Fourth quarter"),
          dep.var.caption  = "A better caption",
          dep.var.labels   = "Flight delay (in minutes)")
 *******************************************************************************************  
   head(df_all_numeric)
   regress_tab8 <- felm(Original_LTV~ ratio+Credit_Score+debt_to_income_ratio+applicantincome+property_value |year, data= final_race_eth_data)
   stargazer(regress_tab8,title="Regression Results",covariate.labels = c("Broadband Penetration", "FICO Score", "Debt to Income","Applicant Income","Property Value"),omit.stat=c("ser"),single.row= TRUE, align=TRUE,type="text", out="New Table8.txt")
   
     regress_tab9 <- felm(interest_rate~ ratio |year, data=final_race_eth_data) 
   stargazer(regress_tab9,title="Regression Results",covariate.labels = c("Broadband Penetration"),single.row= TRUE, align=TRUE,type="text",omit.stat=c("ser"), out="regtab9.txt")
   ------------------ Tab 6 and 9---------------------------
   stargazer(regress_tab6,regress_tab9,title="Regression Results",covariate.labels = c("Broadband Penetration"),single.row= TRUE,omit.stat=c("ser"), align=TRUE,type="latex", out="Tab6and9.txt")
   ---------------------------------------------------
   regress_tab10 <- felm(Original_Combined_LTV~ ratio |countyid+year, data= final_race_eth_data)
   stargazer(regress_tab10,title="Regression Results",covariate.labels = c("Broadband Penetration"),omit.stat=c("ser"),single.row= TRUE, align=TRUE,type="text", out="New tab10.txt")
   
 final_race_eth_data$Credit_Score <- (final_race_eth_data$Credit_Score)/100 
   summary(final_race_eth_data$Credit_Score)
  regress_tab11 <- felm(Original_Combined_LTV~ ratio+Credit_Score+Original_DTI_Ratio+poverty_percentage |year+countyid, data= final_race_eth_data)
   stargazer(regress_tab11,title="Regression Results",single.row= TRUE,covariate.labels = c("Broadband Penetration"),omit.stat=c("ser"), align=TRUE,type="text", out="newtab11.txt")
   
   stargazer(regress_tab10,regress_tab11,title="Univariate(1), multivariate(2)",single.row= TRUE,covariate.labels = c("Broadband Penetration"),omit.stat=c("ser"), align=TRUE,type="latex", out="newtab loan amount compare.txt")
   
   ------------------------- Credit Score affect on ratio---------------------------
   regress_tab7 <- felm(ratio ~ Credit_Score+Original_DTI_Ratio+applicantincome+Original_LTV |countyid+year, data= final_race_eth_data)
   stargazer(regress_tab7,title="Regression Results",covariate.labels = c("FICO Score",)single.row= TRUE, align=TRUE,type="text", out="regtab7.txt")
   -----------
   

----------------------------------Respondent id count-----------------------------
df_respondent_county <-  sqldf("select countyid, countyname, statename, ratio, median_income, absolute_penetration, ratio_ms_usage, poverty_percentage, est_population, year, COUNT(distinct(respondentid)) AS res_count from final_race_eth_data group by  countyid, countyname, statename, ratio, median_income, absolute_penetration, ratio_ms_usage, poverty_percentage, est_population, year;")

df_respondent_county_1 <- df_respondent_county[,c("ratio", "year","countyid","median_income","poverty_perecentage","est_population")]

df_respondent_county <- na.rm(df_respondent_county, cols = c("median_income","poverty_perecentage","est_population"))

nrow(df_respondent_county)
  regress_res_tab5 <- felm(res_count ~ ratio| year , data= df_respondent_county)
  
  stargazer(regress_res_tab5,title=" Regression lending agencies vs internet penetration",single.row= TRUE, align=TRUE,type="latex",covariate.labels = c("Broadband Penetration"),omit.stat=c("ser"), out="regtab5.txt")
 
  
  -------------- Segmented regression demographics-----------------------------------
  
```{r}
distinct_df_demo_info <- sqldf("select distinct derived_race, derived_ethnicity, raceethnicity from  df_all_numeric  where derived_race not in ('Race Not Available','Free Form Text Only')
and derived_ethnicity not in ('Ethnicity Not Available','Free Form Text Only') order by derived_race, derived_ethnicity, raceethnicity ;")
print(distinct_df_demo_info)
```


--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------------


**************************************************************************************8
**********************
```{r}
head(final_race_eth_data)
summary(race_eth_data_1$Credit_Score)
race_eth_data$race_factor <- as.factor(race_eth_data$race_factor)
race_eth_data$ethnicity_factor <- as.factor(race_eth_data$ethnicity_factor)
###################### Table 7 Countyid+year Fixed Effect###############################
 regress_tab07 <- felm(ratio~ Credit_Score+applicantincome+est_population+derived_race+poverty_percentage+derived_ethnicity|countyid+year, data= final_race_eth_data)
   stargazer(regress_tab07,title="Regression Results",dep.var.labels= "Broadband Penetration",covariate.labels = c("FICO Score","Applicant Income", "Population"),single.row= TRUE, align=TRUE,type="text", out="NewTable7.txt")
```

```{r}
>memory.limit()
[1] 1535.875
> memory.limit(size=1000000)
summary(alld)
head(final_race_eth_data)
       -------------------Interest Rate Low Income62k (Include in paper)------------------------------
       df_low_app_income <- sqldf("select * from final_race_eth_data where applicantincome <= 62000 and applicantincome is not null;") 
       regress_tab12 <- felm(interest_rate~ ratio+Credit_Score+debt_to_income_ratio+derived_race|year, data= df_low_app_income)
   stargazer(regress_tab12,title="Regression Results",single.row= TRUE, align=TRUE,type="text", out="regtab12.txt")
```
   
   -------------------Interest Rate High Income135k(Include in paper)------------------------------
```{r}
       df_high_app_income <- sqldf("select * from final_race_eth_data where applicantincome >= 135000 and applicantincome is not null;") 
       regress_tab13 <- felm(interest_rate~ ratio+Credit_Score+debt_to_income_ratio+derived_race|year, data= df_high_app_income)
       stargazer(regress_tab13,title="Regression Results",single.row= TRUE, align=TRUE,type="text", out="regtab13.txt")
   
       
   stargazer(regress_tab12,regress_tab13,title="Low Income(1) vs High Income (2)",single.row= TRUE, align=TRUE,type="text",covariate.labels = c("Broadband Penetration","FICO Score"),omit.stat=c("ser"), out="New low vs high.txt")
   head(final_race_eth_data)
```
   --------------------UPB------------------------------------------
   -----------------Low Income------------------------------------------
```{r}
 head(df_low_app_income)
       regress_tab15 <- felm(amountofloan~ ratio+Credit_Score+debt_to_income_ratio+derived_race|countyid+year, data= df_low_app_income)
   stargazer(regress_tab15,title="Regression Results",covariate.labels = c("Broadband Penetration","FICO Score"),omit.stat=c("ser"),single.row= TRUE, align=TRUE,type="text", out="regtab15.txt")
                              
  -------------------Interest Rate High Income135k------------------------------
       regress_tab16 <- felm(amountofloan ~ ratio+Credit_Score+debt_to_income_ratio+derived_race|countyid+year, data= df_high_app_income)
       stargazer(regress_tab16,title="Regression Results",single.row= TRUE, covariate.labels = c("Broadband Penetration","FICO Score"),omit.stat=c("ser"),align=TRUE,type="text", out="regtab16.txt")
       ------------------ LOW vs High-----------------------------
       
       stargazer(regress_tab15,regress_tab16,title="Unpaid Balance Low_Income(1) vs High_Income(2)",single.row= TRUE, covariate.labels = c("Broadband Penetration","FICO Score"),omit.stat=c("ser"),align=TRUE,type="text", out="New loan amount high vs low.txt")
  
  ------------------------------African American Vs Asian - Low Income------------------
  summary(df_all_diff_med$applicantincome)
  df_low_app_income_aa <- sqldf("select * from df_all_diff_med where derived_race = 'Black or African American'and  applicantincome <= 62000 and applicantincome is not null;") 
   df_low_app_income_asian <- sqldf("select * from df_all_diff_med where derived_race = 'Asian' and applicantincome <= 62000 and applicantincome is not null;") 
   
   regress_tab17 <- felm(abs_int~ ratio_ms_usage+Credit_Score+debt_to_income_ratio|countyid+year, data= df_low_app_income_aa)
   regress_tab18 <- felm(abs_int~ ratio_ms_usage+Credit_Score+debt_to_income_ratio|countyid+year, data= df_low_app_income_asian)
       stargazer(regress_tab17,regress_tab18,title="Low Income Black(1),Asian(2)",single.row= TRUE, align=TRUE,type="text", out="Black vs Asian low incomeregtab18.txt")
       
       ------------------------------African American Vs Asian - High Income------------------
  summary(df_high_app_income_aa$Credit_Score)
  df_high_app_income_aa <- sqldf("select * from df_all_diff_med where derived_race = 'Black or African American'and  applicantincome >= 135000 and applicantincome is not null;") 
   df_high_app_income_asian <- sqldf("select * from df_all_diff_med where derived_race = 'Asian' and applicantincome >= 135000 and applicantincome is not null;") 
   
   regress_tab19 <- felm(abs_int~ ratio_ms_usage+Credit_Score+debt_to_income_ratio|countyid+year, data= df_high_app_income_aa)
   regress_tab20 <- felm(abs_int~ ratio_ms_usage+Credit_Score+debt_to_income_ratio|countyid+year, data= df_high_app_income_asian)
       stargazer(regress_tab19,regress_tab20,title="High Income Black(1),Asian(2)",single.row= TRUE, align=TRUE,type="text", out="black vs Asian high incomeregtab19.txt")
       
       stargazer(regress_tab17,regress_tab19,regress_tab18,regress_tab20, title=" Black(1:Low & 2:High) and Asian(3:Low & 4:High)",covariate.labels = c("Broadband Usage","FICO Score","Debt to Income"),omit.stat=c("ser"),single.row= TRUE, align=TRUE,type="latex", out="Table20.txt")
```
       ----------------same year 2018 , 2019,  2020----------
```{r}
   head(df_app18)    
       df_app18 <- sqldf("select * from final_race_eth_data where  year = 2018;") 
       df_app19 <- sqldf("select * from final_race_eth_data where  year = 2019;") 
   df_app20 <- sqldf("select * from final_race_eth_data where  year = 2020;") 
   
   regress_tab21 <- felm(interest_rate~ ratio+Credit_Score+debt_to_income_ratio|year, data= df_app18)
    regress_tab24 <- felm(interest_rate~ ratio+Credit_Score+debt_to_income_ratio|year, data= df_app19)
   regress_tab22 <- felm(interest_rate~ ratio+Credit_Score+debt_to_income_ratio|year, data= df_app20)
       stargazer(regress_tab21,regress_tab24,regress_tab22,title="2018(1) 2019(2) 2020(3) ",single.row= TRUE, align=TRUE,type="latex",c("Broadband Penetration","FICO Score","Debt to Income"),omit.stat=c("ser"), out="2018_2019_2020.txt")
```

```{r}
----------------------------Diff Median Interest Rate------------------------
summary(df_all_diff_med$Credit_Score)
df_all_diff_med <- sqldf("SELECT a.* , b.med_int_yr, a.interest_rate - b.med_int_yr AS diff_int_yr_med from final_race_eth_data a
LEFT JOIN
(SELECT year, median(interest_rate) as med_int_yr 
from final_race_eth_data group by year) b
ON a.year = b.year;")
df_all_diff_med$abs_int <- abs(df_all_diff_med$diff_int_yr_med)
---------------------------------------------------------------------------------------------
head(df_all_diff_med)
#### Divide Fico by 100
df_all_diff_med$Credit_Score <- (df_all_diff_med$Credit_Score)/100
############### Table 16 abs interest###########################################
regress_tab016 <- felm(abs_int~ ratio+ratio_ms_usage+Credit_Score+debt_to_income_ratio|countyid+year, data= df_all_diff_med)
       stargazer(regress_tab016,title=" diff_med_int ",dep.var.labels="|Interest-Median Interest|",covariate.labels = c("Broadband Penetration","Broadband Usage","Credit Score","Debt to Income"),single.row= TRUE, align=TRUE,type="latex", out="diff interestNewTab16.txt")
```
##################################################################################################
```{r}
head(df_all_diff_med)
head(filter_map_2018_2020)
--------------------Percent change in bbd data join------------------------
df_18_20_change40 <- sqldf("select * from filter_map_2018_2020 where Change1820 >=25 and Change1820 <= 100 ;")
head(df_18_20_change40)

df_reg_40_200_correct_merge <- sqldf("select a.* , b.Change1820 from final_race_eth_data a INNER JOIN df_18_20_change40 b ON a.countyid = b.countyid and a.year=b.year;")
summary(df_reg_40_200_correct_merge$Change1820)
```


       
      BBD 40-200
```{r}
df_reg_40_200_correct_merge$Change1820 <- (df_reg_40_200_correct_merge$Change1820)/100       
regress_tab29 <- felm(interest_rate~ Change1820+Credit_Score+Original_DTI_Ratio+applicantincome+derived_race|year, data= df_reg_40_200_correct_merge)
       stargazer(regress_tab29,title=" Broadband Change>=40%",c("BBD Change","FICO Score"), omit.stat=c("ser"),single.row= TRUE, align=TRUE,type="text", out="new bbd change.txt")
       
```          
--------------------------------Find counties BBD>100----------------------------
```{r}
nrow(df_reg_40_merge)
df_high_bbd_change <- sqldf("select * from df_reg_40_merge where chgper1820>=400 and chgper1820 <= 800 ;")
nrow(df_high_bbd_change)

regress_tab31 <- felm(Original_UPB~ chgper1820+Credit_Score+Original_DTI_Ratio+applicantincome+derived_race|year, data= df_high_bbd_change)
       stargazer(regress_tab31,title=" Broadband Change>=400%" ,single.row= TRUE, align=TRUE,type="text", out="tab31.txt")
```

```{r}
***********************************Garbage***************************************
******************************************************************************************
       *race_eth_data <- sqldf("SELECT * ,
                      CASE ratio WHEN White THEN 0
                      WHEN 'White' THEN 1
                      WHEN 'Native Hawaiian or Other Pacific Islander' THEN 2
                      WHEN 'American Indian or Alaska Native' THEN 3
                      WHEN 'Black or African American' THEN 4
                      ELSE 5 END AS race_factor,
                      CASE derived_ethnicity WHEN 'Not Hispanic or Latino' THEN 0
                      WHEN 'Hispanic or Latino' THEN 1 ELSE 2 END AS ethnicity_factor
                       from race_eth_data_1;")
                       
                       #race_eth_data_1[,race_factor:=ifelse(derived_race %in% c("Asian"),0,
                            ifelse(derived_race %in% c("'White'"),1,
                                   ifelse(derived_race %in% c("Native Hawaiian or Other Pacific Islander"),2,
                                          ifelse(derived_race %in% c("American Indian or Alaska Native"),3,
                                                 ifelse(derived_race %in% c("Black or African American"),4,NA)))))]
  

```
   
       
       